Overt attentional capture by reward-related stimuli overcomes inhibitory suppression

### 2019-04-24 analysis/paper/paper.Rmd
testing travis

keywords          : "attentional capture, reward, suppression, cognitive control"
wordcount         : "6656"

@@

documentclass     : "apa6"
classoption       : "man, a4paper, noextraspace, 11pt"
output            : papaja::apa6_pdf
nocite: |

@@

## Apparatus
Participants were tested using a Tobii TX-300 eye-tracker (sampling frequency 300 Hz), mounted on a 23-inch monitor (1920 $\times$ 1080 resolution, 60 Hz refresh rate). Participants' heads were positioned in a chin rest 60 cm from the screen. Gaze data were down-sampled to 100 Hz for gaze contingent calculations during stimulus presentation, with gaze position in each sample defined as the average position during the preceding 10 ms window. Stimulus presentation was controlled by MATLAB using the Psychophysics Toolbox extensions [@Brainard1997; @Kleiner2007; @Pelli1997]. Experiment scripts, analysis scripts, and raw data are available at (**OSF**).

@@

Statistical analyses were conducted in `r cite_r()` with the afex package  [@R-afex] used to calculate ANOVAs and the emmeans package [@R-emmeans] for follow-up contrasts. Greenhouse-Geisser corrections are reported where appropriate. In cases where a conclusion is drawn on the basis of a null effect, we report the Bayes factor that corresponds to a Bayesian *t*-test using the default Cauchy prior, conducted using the BayesFactor package [@R-BayesFactor].

>>>>

keywords          : "attentional capture, reward, suppression, cognitive control"
wordcount         : "6787"

@@

documentclass     : "apa6"
classoption       : "man, a4paper, noextraspace, 11pt"
output            : papaja::apa6_docx
nocite: |

@@

## Apparatus
Participants were tested using a Tobii TX-300 eye-tracker (sampling frequency 300 Hz), mounted on a 23-inch monitor (1920 $\times$ 1080 resolution, 60 Hz refresh rate). Participants' heads were positioned in a chin rest 60 cm from the screen. Gaze data were down-sampled to 100 Hz for gaze contingent calculations during stimulus presentation, with gaze position in each sample defined as the average position during the preceding 10 ms window. Stimulus presentation was controlled by MATLAB using the Psychophysics Toolbox extensions [@Brainard1997; @Kleiner2007; @Pelli1997].

@@

Statistical analyses were conducted in `r cite_r()` with the afex package  [@R-afex] used to calculate ANOVAs and the emmeans package [@R-emmeans] for follow-up contrasts. Greenhouse-Geisser corrections are reported where appropriate. In cases where a conclusion is drawn on the basis of a null effect, we report the Bayes factor that corresponds to a Bayesian *t*-test using the default Cauchy prior, conducted using the BayesFactor package [@R-BayesFactor]. Experiment scripts, raw data, and a reproducible research compendium of analysis scripts [@marwick2018] are available at https://osf.io/yrdzv/.

### 2019-04-24 analysis/paper/paper.tex
testing travis

\usepackage{amsthm}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\newtheorem{corollary}{Corollary}[section]
\newtheorem{proposition}{Proposition}[section]
\theoremstyle{definition}
\newtheorem{example}{Example}[section]
\theoremstyle{definition}
\newtheorem{exercise}{Exercise}[section]
\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\newtheorem*{solution}{Solution}
\begin{document}
\maketitle

@@

Participants were tested using a Tobii TX-300 eye-tracker (sampling
frequency 300 Hz), mounted on a 23-inch monitor (1920 \(\times\) 1080
resolution, 60 Hz refresh rate). Participants' heads were positioned in
a chin rest 60 cm from the screen. Gaze data were down-sampled to 100 Hz
for gaze contingent calculations during stimulus presentation, with gaze
position in each sample defined as the average position during the
preceding 10 ms window. Stimulus presentation was controlled by MATLAB
using the Psychophysics Toolbox extensions (Brainard, 1997; Kleiner et
al., 2007; Pelli, 1997). Experiment scripts, analysis scripts, and raw
data are available at (\textbf{OSF}).

@@

{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Daniel/Google Drive/Research/vmacfeaturesearch/analysis/figures/Methods_fig}

@@

Statistical analyses were conducted in R (Version 3.5.1; R Core Team,
2018) with the afex package (Singmann, Bolker, Westfall, \& Aust, 2018)
used to calculate ANOVAs and the emmeans package (Lenth, 2018) for
follow-up contrasts. Greenhouse-Geisser corrections are reported where
appropriate. In cases where a conclusion is drawn on the basis of a null
effect, we report the Bayes factor that corresponds to a Bayesian
\emph{t}-test using the default Cauchy prior, conducted using the
BayesFactor package (Morey \& Rouder, 2018).

@@

{\centering \includegraphics[width=0.6\linewidth]{C:/Users/Daniel/Google Drive/Research/vmacfeaturesearch/analysis/figures/omission_plot}

@@

{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Daniel/Google Drive/Research/vmacfeaturesearch/analysis/figures/saccade_plot}

@@

{\centering \includegraphics[width=0.6\linewidth]{C:/Users/Daniel/Google Drive/Research/vmacfeaturesearch/analysis/figures/capture_plot_by_block}

@@

{\centering \includegraphics[width=0.6\linewidth]{C:/Users/Daniel/Google Drive/Research/vmacfeaturesearch/analysis/figures/vincentized_plot}

@@

>>>>

\begin{document}
\maketitle

@@

Participants were tested using a Tobii TX-300 eye-tracker (sampling
frequency 300 Hz), mounted on a 23-inch monitor (1920 \(\times\) 1080
resolution, 60 Hz refresh rate). Participants' heads were positioned in
a chin rest 60 cm from the screen. Gaze data were down-sampled to 100 Hz
for gaze contingent calculations during stimulus presentation, with gaze
position in each sample defined as the average position during the
preceding 10 ms window. Stimulus presentation was controlled by MATLAB
using the Psychophysics Toolbox extensions (Brainard, 1997; Kleiner et
al., 2007; Pelli, 1997).

@@

{\centering \includegraphics[width=0.8\linewidth]{E:/Users/Daniel/Google Drive/Research/vmacfeaturesearch/analysis/figures/Methods_fig}

@@

Statistical analyses were conducted in R (Version 3.5.1; R Core Team,
2018) with the afex package (Singmann, Bolker, Westfall, \& Aust, 2018)
used to calculate ANOVAs and the emmeans package (Lenth, 2018) for
follow-up contrasts. Greenhouse-Geisser corrections are reported where
appropriate. In cases where a conclusion is drawn on the basis of a null
effect, we report the Bayes factor that corresponds to a Bayesian
\emph{t}-test using the default Cauchy prior, conducted using the
BayesFactor package (Morey \& Rouder, 2018). Experiment scripts, raw
data, and a reproducible research compendium of analysis scripts
(Marwick, Boettiger, \& Mullen, 2018) are available at
\url{https://osf.io/yrdzv/}.

@@

{\centering \includegraphics[width=0.6\linewidth]{E:/Users/Daniel/Google Drive/Research/vmacfeaturesearch/analysis/figures/omission_plot}

@@

{\centering \includegraphics[width=0.8\linewidth]{E:/Users/Daniel/Google Drive/Research/vmacfeaturesearch/analysis/figures/saccade_plot}

@@

{\centering \includegraphics[width=0.6\linewidth]{E:/Users/Daniel/Google Drive/Research/vmacfeaturesearch/analysis/figures/capture_plot_by_block}

@@

{\centering \includegraphics[width=0.6\linewidth]{E:/Users/Daniel/Google Drive/Research/vmacfeaturesearch/analysis/figures/vincentized_plot}

@@

\hypertarget{ref-marwick2018}{}
Marwick, B., Boettiger, C., \& Mullen, L. (2018). Packaging data
analytical work reproducibly using R (and friends), e3192v2.
\url{https://doi.org/10.7287/peerj.preprints.3192v2}
